### 2022-06-01 main/chapter_2ljets.tex
add high figure; minor tidyup

\subsection{Stranverse mass \texorpdfstring{$\mttwo$}{mT2}}
\label{sec:2ljets_mt2}
Just as the slepton is a supersymmetric partner to a lepton, the `stransverse'
mass $\mttwo$ is a partner to the `transverse mass' $m_T$
(to be defined shortly),
that is useful in searches for supersymmetric particles.

@@

\clearpage
\subsection{Cheat-sheet}
Uncomfortably many event variables are used to define the regions of this
analysis.
To aid future revision of their meanings, definitions, and references for these
variables are collected here.
All dimensionful quantities are in $\eV[G]$.
\begin{itemize}
\item $\met$: missing transverse momentum
\item $\metsig$: object-based missing transverse momentum significance;\\
described in Section~\ref{sec:2ljets_metsig}
\item $\ptjone$: transverse momentum of the hardest jet%
\vspace{0.5em}
\item $\mll$: invariant mass of the hardest two leptons
\item $\mjj$: invariant mass of the two hardest jets
\item $\mbb$: invariant mass of the two hardest $b$-tagged jets
\item $\mjetone$: mass of the hardest jet
\item $\mttwoll$: `stransverse' mass of the lepton pair with massless invisibles;\\
described in Section~\ref{sec:2ljets_mt2}
\vspace{0.5em}
\item $\rll$: distance in $\eta\textrm{--}\phi$ between the lepton pair
\item $\rjj$: distance in $\eta\textrm{--}\phi$ between the two hardest jets%
\vspace{0.5em}
\item $\njet$: number of signal jets
\item $\nbtag$: number of b-tagged jets;
described in Section~\ref{sec:2ljets_btagging}
\vspace{0.5em}
\item $\dphillmet$: azimuthal angle between the lepton pair and $\ptmiss$
\item $\dphijmet$: azimuthal angle between the hardest jet and $\ptmiss$
\end{itemize}
All of these are physical properties of particles or collections of particles.
Please remember that none is an exact or true value;
all are estimates based on approximate reconstructions.
While this distinction is easy to drop in lax language, it is necessary to
understand the shapes of noisy variables such as $\mjj$ and indeed the
existence of $\metsig$.

@@

\TODO{}
\begin{verbatim}
2ljets_region_design_hist1d_mll_SRHigh.png
2ljets_region_design_hist1d_nbtag_SRHigh.png
\end{verbatim}

@@

>>>>

\subsection{\texorpdfstring{$\mttwo$}{mT2}}
\label{sec:2ljets_mt2}
Just as the slepton is a supersymmetric partner to a lepton, the `stransverse'
mass $\mttwo$ is a partner to the `transverse mass' $m_T$
(to be defined shortly),
that is useful in searches for supersymmetric particles.

@@

\subsection{Cheat-sheet}
Uncomfortably many event variables are used to define the regions of this
analysis.
To aid future revision of their meanings, definitions, and references for these
variables are collected here.
All dimensionful quantities are in $\eV[G]$.
\begin{itemize}
\item $\met$: missing transverse momentum
\item $\metsig$: object-based missing transverse momentum significance;\\
described in Section~\ref{sec:2ljets_metsig}
\item $\ptjone$: transverse momentum of the hardest jet%
\vspace{0.5em}
\item $\mll$: invariant mass of the hardest two leptons
\item $\mjj$: invariant mass of the two hardest jets
\item $\mbb$: invariant mass of the two hardest $b$-tagged jets
\item $\mjetone$: mass of the hardest jet
\item $\mttwoll$: `stransverse' mass of the lepton pair with massless invisibles;\\
described in Section~\ref{sec:2ljets_mt2}
\vspace{0.5em}
\item $\rll$: distance in $\eta\textrm{--}\phi$ between the lepton pair
\item $\rjj$: distance in $\eta\textrm{--}\phi$ between the two hardest jets%
\vspace{0.5em}
\item $\njet$: number of signal jets
\item $\nbtag$: number of b-tagged jets;
described in Section~\ref{sec:2ljets_btagging}
\vspace{0.5em}
\item $\dphillmet$: azimuthal angle between the lepton pair and $\ptmiss$
\item $\dphijmet$: azimuthal angle between the hardest jet and $\ptmiss$
\end{itemize}
All of these are physical properties of particles or collections of particles.
Please remember that none is an exact or true value;
all are estimates based on approximate reconstructions.
While this distinction is easy to drop in lax language, it is necessary to
understand the shapes of noisy variables such as $\mjj$ and indeed the
existence of $\metsig$.

@@

@@

Figure~\ref{fig:2ljets_high_mll_b}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_region_design_hist1d_mll_SRHigh.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_region_design_hist1d_nbtag_SRHigh.png}
\caption{}
\end{subfigure}
\caption{%
SR-High with relaxed selections on (a) $\mll$ or (b) $\nbtag$.
The pure diboson background has very similar shapes to the signals.
Tighter cuts would therefore reduce background and signal yields comparably,
reducing sensitivity.
The significance dropouts in (a) are errors in plotting.
`Significance Z' is the binomial significance with $30\%$ relative background
uncertainty~\cite{cousins2008evaluation}.
Error bars are statistical.
}
\label{fig:2ljets_high_mll_b}
\end{figure}
